---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `pokecolors`

<!-- badges: start -->
<!-- badges: end -->

Color palettes based on [Gen I](https://pokemon.fandom.com/wiki/List_of_Generation_I_Pok%C3%A9mon) and [Gen II](https://pokemon.fandom.com/wiki/List_of_Generation_II_Pok%C3%A9mon) Pokémon for use in R.
Package inspiration from [Barry Mode](https://github.com/BarryMode/pokepalettes) and [Jared Huling](https://github.com/jaredhuling/jcolors).

# Installation

You can install the development version of `pokecolors` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Angela-Jones/pokecolors")
```
# Get color palettes

Access the `pokecolors` color palettes by name or number with `pokecolors()`:

```{r message = FALSE, warning = FALSE}
library(pokecolors)
pokecolors('squirtle')
pokecolors('007')
```

Access a random color palette:

```{r eval = TRUE, message = FALSE, warning = FALSE}
pokecolors('random')
```


# Display color palettes

Color palettes can be displayed using `display_pokecolors()`

## Bulbasaur
```{r}
display_pokecolors("bulbasaur")
```

## Charmander
```{r}
display_pokecolors("charmander")
```

## Squirtle
```{r}
display_pokecolors("squirtle")
```


# Use palettes with `ggplot2`

Now use `scale_color_pokecolors()` with `ggplot2`:

```{r eval = TRUE, message = FALSE, warning = FALSE}
library(ggplot2)
library(gridExtra)
data(morley)
pltl <- ggplot(data = morley, aes(x = Run, y = Speed,
group = factor(Expt),
colour = factor(Expt))) +
    geom_line(size = 2) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "grey97"),
          panel.border = element_blank(),
          legend.position = "bottom")
pltd <- ggplot(data = morley, aes(x = Run, y = Speed,
group = factor(Expt),
colour = factor(Expt))) +
    geom_line(size = 2) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "grey15"),
          legend.key = element_rect(fill = "grey15"),
          panel.border = element_blank(),
          panel.grid.major = element_line(color = "grey45"),
          panel.grid.minor = element_line(color = "grey25"),
          legend.position = "bottom")
grid.arrange(pltl + scale_color_pokecolors(palette = "squirtle"),
             pltd + scale_color_pokecolors(palette = "squirtle"), ncol = 2)
grid.arrange(pltl + scale_color_pokecolors(palette = "charmander"),
             pltd + scale_color_pokecolors(palette = "charmander"), ncol = 2)
```


## More example plots

```{r moreplots}
grid.arrange(pltl + scale_color_pokecolors(palette = "bulbasaur"),
             pltd + scale_color_pokecolors(palette = "bulbasaur"), ncol = 2)
grid.arrange(pltl + scale_color_pokecolors(palette = "pikachu"),
             pltd + scale_color_pokecolors(palette = "pikachu") + 
                 theme(panel.background = element_rect(fill = "grey5")), ncol = 2)
grid.arrange(pltl + scale_color_pokecolors(palette = "magikarp"),
             pltd + scale_color_pokecolors(palette = "magikarp"), ncol = 2)
pltd <- ggplot(data = OrchardSprays, aes(x = rowpos, y = decrease,
group = factor(treatment),
colour = factor(treatment))) +
    geom_line(size = 2) +
    geom_point(size = 4) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "grey15"),
          legend.key = element_rect(fill = "grey15"),
          panel.border = element_blank(),
          panel.grid.major = element_line(color = "grey45"),
          panel.grid.minor = element_line(color = "grey25"),
          legend.position = "bottom")
pltd + scale_color_pokecolors(palette = "jigglypuff")
```


